Modern Graph Generators: A Survey

### 2018-10-20 introduction.tex
Minor corrections

In this survey, we provide a comprehensive overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of graph databases, graph data mining, graph streaming and
machine learning communities, alongside community detection, social
networks and IoT communities. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

@@

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first to survey the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IoT, Telecommunication and graph streaming generators,
and Machine Learning and graph mining generators. However, the literature is still lacking a comprehensive study of
graph generators  for many of the specific subfields mentioned above.

@@

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.
We also point out that this survey is outdated as it does not consider the
graph mining generators that fervently appeared in the last decade.
We fill the gap of more recent social network and graph analytics generators
respectively in Section 3.4 and 3.5.

>>>>

In this survey, we provide a comprehensive overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

@@

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, to provide a global view of the state-of-the-art, we also provide an overview of most commonly used real-world testing graph data sets. And, finally, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first to survey the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover graph databases, Semantic Web, social networks, graph streaming, community detection, and graph data analytics. However, the literature is still lacking a comprehensive study of graph generators  for many of the specific subfields mentioned above.

@@

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.
We also point out that this survey is outdated as it does not consider the
generators that appeared in the last decade.
We fill the gap of more recent social network and graph analytics generators
respectively in Section 3.4 and 3.5.

### 2018-10-20 main.tex
Unification fo terminology
Graphalytics and Graph 500 corrections
Minor corrections

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2016}
\acmMonth{0}

@@

\begin{abstract}
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world linking
properties, or gauging the effectiveness of graph algorithms, techniques
and applications manipulating these data. We consider graph generation
across multiple subfields, such as graph databases, graph data mining,
graph streaming and machine learning communities, alongside community
detection, social networks and IoT communities. Despite the disparate
requirements of modern graph generators throughout these communities, we
analyze them under a common umbrella, reaching out the functionalities, the
practical usage, and their supported operations.
We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.

@@

\keywords{Big Data management, graph data, generators, benchmarks, synthetic data, ...}

@@

\begin{bottomstuff}
This work is supported by ...

Author's addresses:
A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic.
  A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain ;
S. Sakr, University of Tartu,J Liivi 2, Tartu 50409, Estonia.
\end{bottomstuff}

@@

% History dates
\received{August 2016}{September 2016}{December 2016}

>>>>

% Metadata Information
\acmVolume{0}
\acmNumber{0}
\acmArticle{0}
\acmYear{2018}
\acmMonth{0}

@@

\begin{abstract}
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world linking
properties, or gauging the effectiveness of graph algorithms, techniques
and applications manipulating these data. We consider graph generation
across multiple subfields, such as graph databases, Semantic Web, social networks, graph streaming, alongside community detection  and graph data analytics. Despite the disparate
requirements of modern graph generators throughout these communities, we
analyze them under a common umbrella, reaching out the functionalities, the
practical usage, and their supported operations.
We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.

@@

\keywords{Big Data management, graph data, generators, benchmarks, synthetic data}

@@

\begin{bottomstuff}
%This work is supported by ...
Author's addresses:
A. Bonifati, Universit\'{e} Claude Bernard Lyon 1, Liris CNRS Campus La
Doua 23-25 Avenue Pierre de Coubertin, 69622 Villerubanne, France;
I. Holubov\'{a}, Department of Software Engineering, Faculty of Mathematics and Physics, Charles University, Malostransk\'{e} n\'{a}m. 25, 118 00 Praha~1, Czech Republic;
A. Prat-P\'erez, DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Jordi Girona 1-3, 08034 Barcelona, Spain;
S. Sakr, University of Tartu, J Liivi 2, Tartu 50409, Estonia.
\end{bottomstuff}

@@

% History dates
\received{October 2018}{October 2018}{October 2018}
